Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
pass on RQ2
minor tweaks on RQ2

		\bottomrule
	\end{tabular}
	\caption {\ds{} performance on capturing faulty statements, as percentages.}
	\label{tab:red}
\end{table}
\normalsize

@@

        \lang{}            & - & -\\
        \cmath{}           & - & -\\
        %\closure{}          &  & \\
		\chart{}			& - & - \\
        \jtime{}            & - & -\\
        \mockito{}          & - & -\\

		\bottomrule
	\end{tabular}
	\caption {Percentages of cases \ds{} captures faults. Higher is better.}
	\label{tab:ds-cases-captured}
\end{table}
\normalsize

@@

To analyze the impact of dynamic slicing in context, we also compared
\combpar{k} and \sfl{}$^{k}$ considering the same metric, \ie{}, the
number of cases the fault is captured by the technique. Note that the
reason \sfl{}$^{k}$ misses the fault is different compared to
\combpar{k}. It captures the fault if the fault is included within the
top $k$ files; it misses otherwise. Table~\ref{table:fsws} shows
results, indicating that \combpar{k} performs better than \sfl{}$^{k}$
on this metric.\Mar{my opinion is that we should not compare these two
techniques here: 1) it is not the goal of this RQ and 2) this is not
the best metric.} \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
\combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
misses $20$ ($7.7\%$) less faults compared to
\sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
\combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a
significant difference within each technique. Generally, the majority
of faulty statements are found on the $5$ highest ranked faulty
classes. There are few cases where the faulty statements are only
found if the approach considers the first $10$ highest ranked faulty
classes \combpar{10} is the variant of our approach that performs
better \textbf{missing only 23 out of 260 (8.8\%) cases}.

>>>>

@@

		\bottomrule
	\end{tabular}
	\caption {\ds{} performance on capturing faulty statements, as
     percentages. Higher is better.}
	\label{tab:red}
   \label{tab:ds-cases-captured}   
\end{table}
\normalsize

@@

%% \Mar{my
%%   opinion is that we should not compare these two techniques here: 1)
%%   it is not the goal of this RQ and 2) this is not the best metric.}

To analyze the impact of dynamic slicing in context, we also compared
\combpar{k} and \sfl{}$^{k}$ considering the number of cases where the
fault is captured by the technique. Note that the reason \sfl{}$^{k}$
misses the fault is different compared to \combpar{k}. \sfl{}$^{k}$
captures the fault if the fault is included within the top $k$ files;
it misses the fault otherwise. Table~\ref{table:fsws} shows results,
indicating that \combpar{k}, on average, captures more faults compared
to \sfl{}$^{k}$. In only two cases \sfl{}$^{k}$ outperformed
\combpar{k}. These results show that the majority of faulty statements
are found on the $5$ highest ranked faulty classes and that
\combpar{10} is the variant of our approach that performs better
missing only 23 out of the \numFaults\ ($\sim$8.8\%) faults.

%% \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
%% \combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
%% misses $20$ ($7.7\%$) less faults compared to
%% \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
%% \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
%% misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$.

%% repeated...
%%  (2) there are few
%% cases where the faulty statements are only found if the approach
%% considers the first $10$ highest ranked faulty classes
